---
title: "Housing Project"
subtitle: "Draft executive Summary"
format: 
  html:
    error: false
    message: false
    warning: false
    toc: true
    code-fold: true
    math: katex # katex, mathjax, none 
    css: style.css
---

project predictions?
dataset: https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/housing_holdout_test.csv

testing?
https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/housing.csv


```{r}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse,
               tsibble, 
               tsibbledata,
               fable,
               fable.prophet,
               feasts,
               patchwork,
               lubridate,
               rio,
               ggplot2,
               kableExtra, 
               tidyquant,
               plotly)

```



```{r}
df <- read_csv("https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/housing.csv")


```



# Predicted vs. Actual Scatter Plot

Purpose: To provide quantifiable, visual evidence that your model’s predictions are reliable.
What to Include:
Plot actual home prices on one axis and predicted prices on the other.
A 45-degree reference line that represents perfect predictions.
Optionally, annotate the plot with key metrics such as RMSE, MAE, or $R^2$

