---
title: "Housing Project data exploration"
subtitle: "Module 3"
format: 
  html:
    error: false
    message: false
    warning: false
    toc: true
    code-fold: true
    math: katex # katex, mathjax, none 
    css: style.css
---

project predictions?
dataset: https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/housing_holdout_test.csv

testing?
https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/housing.csv


```{r}

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse,
               tsibble, 
               tsibbledata,
               fable,
               fable.prophet,
               feasts,
               patchwork,
               lubridate,
               rio,
               ggplot2,
               kableExtra, 
               tidyquant,
               plotly)

```



```{r}
df <- read_csv("https://raw.githubusercontent.com/byui-cse/cse450-course/master/data/housing.csv")


```



# Predicted vs. Actual Scatter Plot

Purpose: To provide quantifiable, visual evidence that your model’s predictions are reliable.
What to Include:
Plot actual home prices on one axis and predicted prices on the other.
A 45-degree reference line that represents perfect predictions.
Optionally, annotate the plot with key metrics such as RMSE, MAE, or $R^2$

```{r}

ggplot(df, aes(x = yr_built, y = price / 1000)) +
  geom_point() +
  labs(x = "Year Built", y = "Price (thousands)", title = "Scatterplot of Price vs. Year Built") +
  theme_minimal()

```


```{r}

library(ggplot2)
library(dplyr)
library(scales)

df_scaled <- df %>%
  mutate(
    price_scaled = rescale(price, to = c(0, 1)),
    yr_built_scaled = rescale(yr_built, to = c(0, 1))
  )

ggplot(df_scaled, aes(x = yr_built_scaled, y = price_scaled)) +
  geom_point() +
  labs(x = "Year Built (Scaled)", y = "Price (Scaled)", 
       title = "Scatterplot of Scaled Price vs. Scaled Year Built") +
  ylim(0, 0.5) +
  theme_minimal()


```



```{r}
# average price giving the year it was built
# This is not a good one since sale year is 2014 and 2015
# ok it is good, as some correlation can be found.
library(dplyr)

df_avg_price <- df |>
  group_by(yr_built) |>
  summarise(avg_price = mean(price, na.rm = TRUE))

# View result
df_avg_price



```



```{r}
# this one is good
# it plots the average price per zip code

library(dplyr)

df_avg_price_zip <- df |>
  group_by(zipcode) |>
  summarise(avg_price = mean(price, na.rm = TRUE))


```

```{r}

library(dplyr)

df_count_price_zip <- df |>
  group_by(zipcode) |>
  summarise(avg_price = mean(price, na.rm = TRUE))

```


```{r}
library(dplyr)
library(lubridate)

df_weekly_counts <- df %>%
  mutate(week = floor_date(as.Date(date), unit = "week")) %>%
  group_by(week) %>%
  summarise(sold = n())


ggplot(df_weekly_counts, aes(x = week, y = sold)) +
  geom_line() +
  labs(x = "Date", y = "Sold", title = "Sold homes per week") +
  theme_minimal()

```



```{r}
# this counts the number of homes sold per month
library(dplyr)
library(lubridate)

df_m_counts <- df %>%
  mutate(month = floor_date(as.Date(date), unit = "month")) %>%
  group_by(month) %>%
  summarise(sold = n(), .groups = "drop")

ggplot(df_m_counts, aes(x = month, y = sold)) +
  geom_line() +
  labs(x = "Date", y = "Sold", title = "Sold homes per week") +
  theme_minimal()


df_m_counts

```






```{r}



```













































































































































































































spacer